---
title: "Female Pulse"
author: "Luit Deka"
format: html
execute: 
  echo: false
---

```{r}
#| message: false
library(primer.data)
library(tidyverse)
```

```{r}
x <- nhanes |>
  select(pulse, gender) |>
  drop_na() |>
  filter(gender == "Female")
````

#Wisdom 

Predictive or Causal: Predictive
Unit: Each Student
Outcome: Pulse
Covariates: Age, Weight, bmi, heights, sleep
Preceptor Table: 
Validity: Not all units may be students. Education is NA. BMI, weight and Height measurements are not clear. BMI and weight may not be accurately measured. Different devices to measure.

Outcome to Preceptor Table answer to question

#Justice

Representativeness or the lack thereof, is the relationship, among the rows in the Population Table, between our data and the other rows. Ideally, we would like our data to be a random sample from the population. Sadly, this is almost never the case.

Unconfoundedness means that the treatment assignment is independent of the potential outcomes, when we condition on pre-treatment covariates. This assumption is only relevant for causal models. We write that a model is “confounded” if this is not true. The easiest way to ensure unconfoundedness is to randonly assign treatment.

Representativeness: Test-take(Stress level)
Stability: All participants are in the past
Unconfoundedness: Does not Apply!
Formula: He

#Courage

pulse: 

```{r}
x |>
  ggplot(aes())
```

